Supplementary Materials

### 2024-11-20 manuscript.Rmd
Move everything to top directory

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
## libreoffice --headless --convert-to pdf manuscript.docx
title: "Assessing the Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
#    md_document: default
#    bookdown::pdf_document2:
#      toc:false
#      number_sections:false
---

@@

## Corresponding author
Martin Gerdin Wärnberg (MGW)`r insert_orcid_link("0000-0001-6069-4794")`

@@

##### Debojit Basak `r insert_orcid_link("90000-0002-8378-9689")`
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Johanna Berg (JB) `r insert_orcid_link("0000-0001-7553-7337")` <!-- Accepted -->
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee (SC) `r insert_orcid_link("0000-0002-9460-108X")` <!-- Accepted -->
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Felländer-Tsai (LFT) `r insert_orcid_link("0000-0003-0693-6080")` <!-- Accepted -->
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Geeta Ghag (GG) `r insert_orcid_link("0000-0001-5561-362X")`
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Monty Khajanchi (MK)`r insert_orcid_link("0000-0002-0898-6391")` <!-- Accepted -->
WHO Collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

Seth G. S. Medical College and K.E.M. Hospital, Mumbai, India.

##### Tamal Khan 
Senior Research fellow, All India Institute of Medical Sciences, New Delhi, India.

##### Catherine Juillard (CJ) `r insert_orcid_link("0000-0003-0847-8933")` <!-- Accepted -->
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

##### Vipul Nandu `r insert_orcid_link("0000-0002-3366-5610")` 
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Nobhojit Roy (NR) `r insert_orcid_link("0000-0003-2022-7416")`
Program for Global Surgery and Trauma, The George Institute of Global Health, New Delhi, India.

@@

##### Rajdeep Singh (RS) `r insert_orcid_link("0000-0001-6593-2624")` <!-- Accepted -->
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni (KDS) `r insert_orcid_link("0000-0003-1214-4119")` <!-- Accepted -->
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS) `r insert_orcid_link("0000-0001-5424-7111")` <!-- Accepted -->
Division of Surgery and Oncology, Department of Clinical Science, Intervention and Technology (CLINTEC),  and Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

Trauma life support Effectiveness Research Network (TERN) collaborators:

@@

##### Anirban Chatterjee (AC)
Department of Orthopaedic Sciences, Medica Superspecialty Hospital, Kolkata, India.

@@

<!--
## Word Count
4494
 -->

@@

MGW conceived of the study, performed the analysis and drafted and revised the manuscript. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH,
MGW, MK, NR, PB, PP, RS, SD, and VK contributed to the design of the
study. MGV, DKV, KDS, and MK drafted the first version of the
protocol. AG, HS, and SD drafted the first version of the patient and
public involvement activities. JB and PP drafted the first versions of
the data management sections and wrote the data management plan. PB
and PP drafted the first versions of the statistical analysis
section. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH, MGW, MK, NR, PB,
PP, RS, SC, SD, and VK contributed to the refinement of the
protocol. DB, JB, SC, LFT, GG, MK, TK, CJ, NR, RS, KDS, LS and VP interpreted the results and revised the manuscript. AR, AC, C, DK, GG, MK, MT, VK and VP are representatives of participating hospitals.

>>>>

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
## libreoffice --headless --convert-to pdf manuscript.docx
title: "Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
#    md_document: default
#    bookdown::pdf_document2:
#      toc:false
#      number_sections:false
---

@@

## Corresponding author

##### Martin Gerdin Wärnberg, MD, PhD (MGW) `r insert_orcid_link("0000-0001-6069-4794")`

@@

##### Debojit Basak, MS `r insert_orcid_link("90000-0002-8378-9689")` <!-- Accepted, debojit88@gmail.com -->
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Johanna Berg, MD (JB) `r insert_orcid_link("0000-0001-7553-7337")` <!-- Accepted, johanna.berg@ki.se -->
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee, MBBS, MS (SC) `r insert_orcid_link("0000-0002-9460-108X")` <!-- Accepted, dr_shamita@yahoo.com -->
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Felländer-Tsai, MD, PhD (LFT) `r insert_orcid_link("0000-0003-0693-6080")` <!-- Accepted -->
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Geeta Ghag (GG), MBBS, MS `r insert_orcid_link("0000-0001-5561-362X")` <!-- Accepted, geetaghag@hotmail.com -->
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Catherine Juillard, MD, MPH (CJ) `r insert_orcid_link("0000-0003-0847-8933")` <!-- Accepted, cjuillard@mednet.ucla.edu -->
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

##### Monty Khajanchi, MBBS, MS (MK) `r insert_orcid_link("0000-0002-0898-6391")` <!-- Accepted, monta32@gmail.com -->
Seth G. S. Medical College and K.E.M. Hospital, Mumbai, India.

##### Tamal Khan, MSc (TK) <!-- Accepted, tamal.khan440@gmail.com -->
Senior Research fellow, All India Institute of Medical Sciences, New Delhi, India.

##### Vipul Nandu, MBBS, MS (VN) `r insert_orcid_link("0000-0002-3366-5610")`  <!-- Accepted, dr.vipulnandu@gmail.com -->
Department of Surgery, HBT Medical College And Dr. R N Cooper Municipal General Hospital, Mumbai, India.

##### Nobhojit Roy, MBBS, MS, PhD (NR) `r insert_orcid_link("0000-0003-2022-7416")` <!-- Accepted, nroy@georgeinstitute.org.in -->
Program for Global Surgery and Trauma, The George Institute of Global Health, New Delhi, India.

@@

##### Rajdeep Singh, MBBS, MS (RS) `r insert_orcid_link("0000-0001-6593-2624")` <!-- Accepted, rajdeep.mamc@gmail.com -->
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni, MBBS, MD (KDS) `r insert_orcid_link("0000-0003-1214-4119")` <!-- Accepted, kdsoni111@gmail.com -->
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer, MD, PhD (LS) `r insert_orcid_link("0000-0001-5424-7111")` <!-- Accepted, lisa.strommer@ki.se -->
Division of Surgery and Oncology, Department of Clinical Science, Intervention and Technology (CLINTEC), and Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

Trauma life support Effectiveness Research Network (TERN) collaborators.

<!--

@@

##### Anirban Chatterjee (AC) <!-- Accepted -->
Department of Orthopaedic Sciences, Medica Superspecialty Hospital, Kolkata, India.

@@

## Word Count
2836

@@

MGW conceived of the study, performed the analysis and drafted and revised the manuscript. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH, MK, NR, PB, PP, RS, SD, and VK contributed to the design of the
study. MGV, DKV, KDS, and MK drafted the first version of the
protocol. AG, HS, and SD drafted the first version of the patient and
public involvement activities. JB and PP drafted the first versions of
the data management sections and wrote the data management plan. PB
and PP drafted the first versions of the statistical analysis
section. AG, AM, CJ, DKV, HS, JB, KDS, LFT, LS, MH, MGW, MK, NR, PB,
PP, RS, SC, SD, and VK contributed to the refinement of the
protocol. DB, JB, SC, LFT, GG, MK, TK, CJ, NR, RS, KDS, LS and VP interpreted the results and revised the manuscript. AR, AC, C, DK, GG, MK, MT, VK and VP are representatives of participating hospitals.

### 2024-11-20 outcome-tables.Rmd
Move everything to top directory

# Results with 75% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

@@

## Outcomes in all patients before training, by treatment arm

@@

## Outcomes in all patients after training, by treatment arm

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

@@

# Results with 85% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

@@

## Outcomes in all patients before training, by treatment arm

@@

## Outcomes in all patients after training, by treatment arm

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

@@

# Results with 95% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

@@

## Outcomes in all patients before training, by treatment arm

@@

## Outcomes in all patients after training, by treatment arm

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

>>>>

# Results with 75% confidence intervals (CI)

## Outcomes in all patients during the entire study period, by treatment arm(75% CI)

@@

## Outcomes in all patients before training, by treatment arm(75% CI)

@@

## Outcomes in all patients after training, by treatment arm(75% CI)

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(75% CI)

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(75% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS(75% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC(75% CI)

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC(75% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS(75% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC(75% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC(75% CI)

@@

# Results with 85% confidence intervals (CI)

## Outcomes in all patients during the entire study period, by treatment arm(85% CI)

@@

## Outcomes in all patients before training, by treatment arm(85% CI)

@@

## Outcomes in all patients after training, by treatment arm(85% CI)

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(85% CI)

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(85% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS(85% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC(85% CI)

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC(85% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS(85% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC(85% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC(85% CI)

@@

# Results with 95% confidence intervals (CI)

## Outcomes in all patients during the entire study period, by treatment arm(95% CI)

@@

## Outcomes in all patients before training, by treatment arm(95% CI)

@@

## Outcomes in all patients after training, by treatment arm(95% CI)

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(95% CI)

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms(95% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS(95% CI)

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC(95% CI)

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC(95% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS(95% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC(95% CI)

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC(95% CI)

### 2024-11-20 supplementary-materials.Rmd
Move everything to top directory

---
title: Supplementary Materials
subtitle: "Assessing the Feasibility of a Pilot Cluster Randomised Trial of the Effect of Trauma Life Support Training: A Pilot Study"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
      toc: true
---

>>>>

---
## Rscript -e "rmarkdown::render('supplementary-materials.Rmd')"
## libreoffice --headless --convert-to pdf supplementary-materials.docx
title: Supplementary Materials
subtitle: "Assessing the Feasibility of a Pilot Cluster Randomised Trial of the Effect of Trauma Life Support Training: A Pilot Study"
output:
    bookdown::word_document2:
      number_sections: false
      reference_docx: "reference.docx"
      toc: true
---
